---
output: 
  html_document:
    include:
      after_body: footer.html
knit: (function(inputFile, encoding) { 
      out_dir <- 'docs';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'index.html')) })
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE)
```

###  Gender Systems in Nakh-Daghestaninan languages {.tabset .tabset-fade .tabset-pills}

Download database of gender systems: [.csv](https://raw.githubusercontent.com/kartozia/spatial_analysis_of_NakhDaghestanian_languages/master/data/noun_classes.csv)

Download dataset of Nakh-Daghestanian settlements: [.csv](https://raw.githubusercontent.com/kartozia/spatial_analysis_of_NakhDaghestanian_languages/master/data/allvillages_v2.csv)

#### about database
Database contains information about structure of gender systems in Nakh-Daghestaninan languages.

* Language - name of language or its dialect
* Class — number of gender in a language
* Sg - gender marker in singular
* PL - gender marker in plural
*	S_label - source label, how gender marked in the source (e.g. Roman numbers)
* label - custom labels:
    *	F for gender where all women and only women are included
    *	M for gender where all men and only men are included
    *	N a third gender that includes everything except F and M (is the only such gender)
*	semantic - semantic description of the gender from the source
*	source - info source, e.g. [Ihilov 1967: 9-15]
*	comments - for any extra info one would like to mention

Number of genders in Nakh-Daghestanian languages:
```{r}
library(tidyverse)
library(lingtypology)
noun <- read.csv("https://raw.githubusercontent.com/kartozia/spatial_analysis_of_NakhDaghestanian_languages/master/data/noun_classes.csv", sep = ";")
names(noun)[1] <- "index"
df <- read.csv("https://raw.githubusercontent.com/kartozia/spatial_analysis_of_NakhDaghestanian_languages/master/data/allvillages_v2.csv", sep = ";")
df <- as_tibble(df)
map.feature(languages = df$Language,
            latitude = as.numeric(df$Lat),
            longitude = as.numeric(df$Lon),
            features = df$classes,
            label = paste(df$Language, df$dialect),
            popup = df$EngNames,
            tile = 'CartoDB.Positron',
            color = "viridis",
            width = 3, stroke.radius = 3)
```

#### search
```{r}
library(DT)
datatable(noun[, -10], filter = 'top', rownames = FALSE, options = list(pageLength = 20, dom = 'tip'), escape = FALSE)
```

#### spatial autocorrelation
Spatial autocorrelation was calculated globally and localy in order to detect any spatial patterns in distribution of gender systems. 
Used tests:

* Moran's *I* — gloabl spatial autocorrelation
* Getis and Ord *Gi\** — local spatial autocorrelation

First Moran's *I* is calculated:
``` {r warning=FALSE, message=FALSE}
library(tidyverse)
library(lingtypology)
library(spdep)
df <- read.csv("https://raw.githubusercontent.com/kartozia/spatial_analysis_of_NakhDaghestanian_languages/master/data/allvillages_v2.csv", sep = ";")
df <- as_tibble(df)
sp_df <- df[,c(2,3,4,8,9,12,13)]
sp_df <- unique(sp_df)
sp_df[is.na(sp_df)] <- 0
space <- cbind(as.numeric(sp_df$Lon), as.numeric(sp_df$Lat))
test <- knn2nb(knearneigh(space, k=10, longlat = TRUE), row.names = sp_df$index)
final <- include.self(test)
ww <- nb2listw(final, style='B', zero.policy = TRUE)
moran.test(sp_df$classes, ww,randomisation=FALSE)
```
Then Moran's *I* Monte Carlo simulation (n = 1000) to verify the results:
``` {r}
moran.mc(sp_df$classes, ww, nsim=999)
```
To measure spatial autocorrelation a spatial weight matrix is created. Distance is calculated with k-nearest neighbors algorithm. *K=10* is chosen.
Calculating and mapping Getis and Ord *Gi\**:
``` {r}
localGvalues <- localG(x = as.numeric(sp_df$classes), listw = ww, zero.policy = TRUE)
localGvalues <- round(localGvalues,3)
sp_df1 <- sp_df
sp_df1$values <- localGvalues
sp_df1 <- sp_df1[,-1]
map.feature(languages = sp_df1$Language,
            latitude = as.numeric(sp_df1$Lat),
            longitude = as.numeric(sp_df1$Lon),
            features = as.numeric(sp_df1$values),
            label = paste(sp_df1$Language,sp_df1$classes,sp_df1$dialect),
            popup = sp_df1$EngNames,
            tile = 'CartoDB.Positron',
            color= "viridis",
            width = 3.5, stroke.radius = 3)
```


Getis and Ord *Gi\**, if *k=5*:
``` {r warning=FALSE}
test <- knn2nb(knearneigh(space, k=5, longlat = TRUE), row.names = sp_df$index)
final <- include.self(test)
ww <- nb2listw(final, style='B', zero.policy = TRUE)
localGvalues <- localG(x = as.numeric(sp_df$classes), listw = ww, zero.policy = TRUE)
localGvalues <- round(localGvalues,3)
sp_df2 <- sp_df
sp_df2$values <- localGvalues
sp_df2 <- sp_df2[,-1]
map.feature(languages = sp_df2$Language,
            latitude = as.numeric(sp_df2$Lat),
            longitude = as.numeric(sp_df2$Lon),
            features = as.numeric(sp_df2$values),
            label = paste(sp_df2$Language,sp_df2$classes,sp_df2$dialect),
            popup = sp_df2$EngNames,
            tile = 'CartoDB.Positron',
            color= "viridis",
            width = 3.5, stroke.radius = 3)
```



Getis and Ord *Gi\**, if *k=50*:
``` {r warning=FALSE}
test <- knn2nb(knearneigh(space, k=50, longlat = TRUE), row.names = sp_df$index)
final <- include.self(test)
ww <- nb2listw(final, style='B', zero.policy = TRUE)
localGvalues <- localG(x = as.numeric(sp_df$classes), listw = ww, zero.policy = TRUE)
localGvalues <- round(localGvalues,3)
sp_df3 <- sp_df
sp_df3$values <- localGvalues
sp_df3 <- sp_df3[,-1]
map.feature(languages = sp_df3$Language,
            latitude = as.numeric(sp_df3$Lat),
            longitude = as.numeric(sp_df3$Lon),
            features = as.numeric(sp_df3$values),
            label = paste(sp_df3$Language,sp_df3$classes,sp_df3$dialect),
            popup = sp_df3$EngNames,
            tile = 'CartoDB.Positron',
            color= "viridis",
            width = 3.5, stroke.radius = 3)
```

#### references
```{r}
library(RefManageR)
BibOptions(check.entries = FALSE)
bib <- ReadBib("./docs/bibliography.bib")
vec <- as.vector(noun$source_bibtex)
df <- data.frame(lang = noun$Language,
                 citation = vec,
                 stringsAsFactors = FALSE)

df <- unique(df)
df$citation_text <- sapply(df$citation, function(i){Cite(bib, i)})
PrintBibliography(bib)
```