---
output: 
  html_document:
    include:
      after_body: footer.html
knit: (function(inputFile, encoding) { 
      out_dir <- 'docs';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'index.html')) })
---

```{r setup, include=FALSE, warning=F}
knitr::opts_chunk$set(echo=FALSE, message=FALSE)
```

###  Gender Systems in Nakh-Daghestaninan languages {.tabset .tabset-fade .tabset-pills}
Some characters may be displayed incorrectly.

Download database: [.csv](https://raw.githubusercontent.com/kartozia/spatial_analysis_of_NakhDaghestanian_languages/master/data/noun_classes.csv)

#### about database
Database contains information about structure of gender systems in Nakh-Daghestaninan languages.

* Language - name of language or its dialect
* Class — number of gender in a language
* Sg - class marker in singular
* PL - class marker in plural
*	S_label - source label, how class marked in the source (e.g. Roman numbers)
* label - custom labels:
    *	F for class where all women and only women are included
    *	M for class where all men and only men are included
    *	N a third class that includes everything except F and M (is the only such class)
*	semantic - semantic description of the class from the source
*	source - info source, e.g. [Ihilov 1967: 9-15]
*	comments - for any extra info one would like to mention


```{r}
#bibliography <- read.csv("bibliography.csv", sep = "\t", na.strings = "")
noun <- read.csv("https://raw.githubusercontent.com/kartozia/spatial_analysis_of_NakhDaghestanian_languages/master/data/noun_classes.csv", sep = ";")
names(noun)[1] <- "index"
#library(lingtypology)
#map.feature(unique(bibliography$language),
 #           label = unique(bibliography$language),
  #          label.hide = TRUE,
   #         color = "blue")
```

#### search
```{r}
library(DT)
datatable(noun[, -10], filter = 'top', rownames = FALSE, options = list(pageLength = 20, dom = 'tip'), escape = FALSE)
```

#### bibliography
```{r}
library(RefManageR)
BibOptions(check.entries = FALSE)
bib <- ReadBib("./docs/bibliography.bib")
vec <- as.vector(noun$source_bibtex)
df <- data.frame(lang = noun$Language,
                 citation = vec,
                 stringsAsFactors = FALSE)

df <- unique(df)
df$citation_text <- sapply(df$citation, function(i){Cite(bib, i)})
#datatable(bibliography, filter = 'top', rownames = FALSE, options = list(pageLength = 20, autoWidth = FALSE), escape = FALSE)
PrintBibliography(bib)
```